How to Avoid OOTA Without Really Trying

### 2024-10-03 paper/ootavacuous.tex
ootavacuous: Add mention of tooling to Section 7.1
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

One drawback of our definition of semantic dependency is that it is only
relative to a specific compiler or implementation.
This may strike some readers as wishy-washy and avoiding the real
problem, in that a given piece of code should either contain or not
contain a semantic dependency, independent of the implementation used to
run it.

>>>>

One drawback of our definition of semantic dependency is that it is only
relative to a specific compiler or implementation.
This may strike some readers (especially those implementing tooling)
as wishy-washy and avoiding the real problem, in that a given piece
of code should either contain or not contain a semantic dependency,
independent of the implementation used to run it.
